A survey of HTTP caching options on the open Web

### 2015-01-12 sanity/paper1.tex
small
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@963 43ef1190-90fd-4dd7-a769-d0121f02b80e
some references
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@964 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass{llncs}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{wrapfig}
\usepackage{appendix}

@@

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo}%\inst{1}}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}

%\subtitle{---Unpublished Working Draft, do not circulate---}

@@

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \todo{ref} is entirely devoted to the topic, and
RFC7232 defines conditional requests, which is also important when
constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web \todo{ref}
discusses caching throughout, and the definition of the
Representational State Transfer (REST) architectural style \todo{ref}
is partly motivated from the requirement to implement efficient
caching. We also note that caching in the Internet infrastructure,
through so-called Content Delivery Networks, is both a large business
area and something that could provide great value to the Semantic Web
community.

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. Our reasons
to do this include
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}

@@

LDF\todo{ref} asserted that SPARQL query caching is only possible on a
per-query basis, but future research should challenge this
assumption. With this in mind, if reasoning is not involved, we note
that ontologies are not relevant to query answering since they usually
occur in bound terms. It is interesting to understand caching when
this is not the case. Moreover, many ontologies are maintained by a
small group of humans and change seldomly.

@@

The \todo{ref dyldo} Dynamic Linked Data Observatory (DyLDO)
performed, and continue to do so, of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.

LDF\todo{ref paper1} claims to take advantage of caching and contrasts
this with the unavailability of SPARQL query caches, and claims this is
an architectural problem.

The implications of HTTP for query caches has been discussed by
\todo{ref kasei}. In \todo{marin, Auer} the authors implemented a
reverse proxy that controlled the changes to the dataset, and
therefore could

A general caching approach is given in \todo{Caching intermediate
  result of sparql queries}.

\todo{fast vs. fresh} didn't consider caching in the sense we do, they
rather prefetch an entire dataset to a local store and based on
heuristics tried to determine which parts of the query should be
evaluated remotely and locally.

\todo{cache or not} explored when caching had a positive effect on
complex SPARQL queries.

In the broader Web literature, \todo{Revisiting Cacheability
in Times of User Generated Content} analysed the value of caching
based anonymized traces of actual Web usage at a major Internet
Service Provider.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others. To
test this hypothesis, we create two so-called \emph{contigency
  tables}\todo{ref}. This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is only to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.

Using the statistics system R\todo{ref}, we use a statistical test,
namely Pearson's $\chi^2$ test with simulated \pvalue (based on 10000
replicates). The simulation is done using a Monte Carlo method to
compensate for the fact that many servers will not expose caching
headers at all, an issue that would otherwise violate the underlying
assumptions of the test.

>>>>

\documentclass{llncs}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{wrapfig}
\usepackage{appendix}

@@

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}

\subtitle{---Unpublished Working Draft, do not circulate---}

@@

Caching has been given a prominent place in the foundational documents
of the World Wide Web. Out of the 6 documents that make up the HTTP
1.1 standard, RFC7234 \cite{rfc7234} is entirely devoted to the topic,
and RFC7232 \cite{rfc7232} defines conditional requests, which is also
important when constructing caches. As the former notes:
\begin{quote} 
  The goal of caching in HTTP/1.1 is to significantly improve
  performance by reusing a prior response message to satisfy a current
  request.
\end{quote}
Furthermore, the Architecture of the World Wide Web
\cite{Jacobs:04:AWW} discusses caching throughout, and the definition
of the Representational State Transfer (REST) architectural style
\cite{Fielding_2000_Architectural-Styles} is partly motivated from the
requirement to implement efficient caching. We also note that caching
in the Internet infrastructure, through so-called Content Delivery
Networks, is both a large business area and something that could
provide great value to the Semantic Web community.

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. Our reasons
to do this include\todo{formulate as contributions?}
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}

@@

In \cite{ldf1}, it was asserted that SPARQL query caching is only
possible on a per-query basis, but future research should challenge
this assumption. With this in mind, if reasoning is not involved, we
note that ontologies are not relevant to query answering since they
usually occur in bound terms. It is interesting to understand caching
when this is not the case. Moreover, many ontologies are maintained by
a small group of humans and change seldomly.\todo{not particularly clear}

@@

The \cite{dyldo2} Dynamic Linked Data Observatory (DyLDO)
performed, and continue to do so, of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.

Linked Data Fragments \cite{ldf1} claims to take advantage of caching
and contrasts this with the unavailability of SPARQL query caches, and
claims this is an architectural problem.

The implications of HTTP for query caches has been discussed by
\cite{kaseicache}. In \cite{sparqlproxy} the authors implemented a
reverse proxy that controlled the changes to the dataset, and
therefore could make sure the proxy had all the information needed to
determine freshness. We are interested in the situation where the
changes cannot be controlled.

A general caching approach is given in \cite{yang2011caching}.  In
\cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetch an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL queries.

In the broader Web literature, \cite{ager2010revisiting} analysed the
value of caching based anonymized traces of actual Web usage at a
major Internet Service Provider.

@@

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others. To
test this hypothesis, we create two so-called \emph{contigency
  tables}\cite{kn:bj}. This formalism is suited to see if the
distribution of  \httph{Server} headers are different for those implementations that
offer caching headers from those that don't. Intuitively, we expect
these distributions to be similar, ``long-tail'' distributions, i.e. a
handful of servers are used by a large number of projects, and then it
falls off rapidly, and so, some servers are used only by very
few. Likewise, it is only to be expected that only a few projects have
given caching enough attention, but that they account for the majority
of the support. The question is if the presence of caching headers is
merely a matter of proportion, or if there are some that have given it
more attention, but still is in relatively little use.

Using the statistics system R\cite{kn:r}, we use a statistical test,
namely Pearson's $\chi^2$ test with simulated \pvalue (based on 10000
replicates). The simulation is done using a Monte Carlo method to
compensate for the fact that many servers will not expose caching
headers at all, an issue that would otherwise violate the underlying
assumptions of the test.
